Material Methods

### 2019-09-18 doc/MatMeth.Rmd
started thinking about results. more updates to material methods

---
title: "Material Metohds"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_depth: '5'
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '5'
bibliography: refs_MatMeth.bib
---

```{r set.up, echo=FALSE}
#set wd
#load datafile
```

@@

To access natural genetic variation for *Mus musculus*, wild derived inbred strains were used. The Mus musculus PWD/PhJ, PERC/Eij, WSB/EiJ, LEWE/EiJ, MSM/MsJ, MOLF/EiJ, CAST/EiJ, CZECHII/EiJ were purchased from Jackson labs (Maine, USA). The strains of KAZ/TUA, TOM/TUA, AST/TUA, and HMI/TUA were cryo-derived from Biological Resource Center (BRC) at Riken (Ibaraki, Japan).  (https://en.brc.riken.jp/).
The related species of *Mus caroli* CAROLI/EiJ and *Mus spretus* SPRET/EiJ were purchased from Jax labs (https://www.jax.org) and *Mus spicilegus* SPIC/Eij from Riken.

@@

Over the course of data collection some breeding colonies / mice were moved from facilities. Additionally the GI strain was kept at a separate facility.  (evidence for environmental (room) effect on (MLH1 / SC lengths / a variety of meiotic traits was tested for. We observed no effect, Supplemental figure))

@@

The only difference between preparation of spermatocyte and oocyte spreads was the volumns of the hypotonic buffer was 300$\mul instead of 3ml.

@@

<!--
Meiocyte spreads were made following [@peters_1997]. For testes the tunica was removed and whole testes was incubated in 3ml of hypotonic solution for 45min. For ovaries after dissection, the pair of ovaries were decapsulated in cold PBS and both were incubated in 300ul of hypotonic solution for 45 min.

After incubation, gonads were transferred to sucrose solution -for mastication to make a cell slurry which was transferred to 80ul of 2% PFA solution. Cells were fixed in this solution and dried in a humid chamber at room temperature overnight. The next morning, slides were treated with a photoflow (Kodak, cite) wash.
-->

@@

@@

Images of cells were capture on Axio-2 microscope.

@@

Hand measures data set generated by using ImageJ.

total Sc was measured (Rwang et al 2019)

Bivalent level measure were done (Peterson et al 2019)

@@

Statistical analysis was performed in R (version and cite).

@@

 $X \sim MLH1_mouse average ~ sex * subsp + random(strain)+ strain*sex+$\xi

@@

the random effect of strain in this model can be interpreted as the average standard deviation due to the random strain effect
and sex*strain,

>>>>

---
title: "Material Methods"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_depth: '5'
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '5'
bibliography: refs_MatMeth.bib
---

```{r set.up, echo=FALSE}
#set wd
#load datafile

#common bugs
#html won't compile -- one of my citations in bib was breaking things
```

@@

To access natural genetic variation for *Mus musculus*, wild derived inbred strains were used. The Mus musculus PWD/PhJ, PERC/Eij, WSB/EiJ, LEWE/EiJ, MSM/MsJ, MOLF/EiJ, CAST/EiJ, CZECHII/EiJ were purchased from Jackson labs (Maine, USA). The strains of KAZ/TUA, TOM/TUA, AST/TUA, and HMI/TUA were cryo-derived from Biological Resource Center (BRC) at Riken (Ibaraki, Japan).  (https://en.brc.riken.jp).
The related species of *Mus caroli* CAROLI/EiJ and *Mus spretus* SPRET/EiJ were purchased from Jax labs (https://www.jax.org) and *Mus spicilegus* SPIC/Eij from Riken.

@@

Over the course of data collection some breeding colonies  mice were moved from facilities. Additionally the GI strain was kept at a separate facility.  (evidence for environmental (room) effect on (MLH1 / SC lengths / a variety of meiotic traits was tested for. We observed no effect, Supplemental figure))

@@

The only difference between preparation of spermatocyte and oocyte spreads was the volumns of the hypotonic buffer was 300 u l instead of 3ml.

@@

Meiocyte spreads were made following [@peters_1997]. For testes the tunica was removed and whole testes was incubated in 3ml of hypotonic solution for 45min. For ovaries after dissection, the pair of ovaries were decapsulated in cold PBS and both were incubated in 300ul of hypotonic solution for 45 min.

After incubation, gonads were transferred to sucrose solution -for mastication to make a cell slurry which was transferred to 80ul of 2% PFA solution. Cells were fixed in this solution and dried in a humid chamber at room temperature overnight. The next morning, slides were treated with a photoflow (Kodak, cite) wash.

@@

Explain list recipes for DMC1 since these haven't been listed before

@@

Images of cells were capture using a Zeiss Axioplan 2 microscope with AxioLab camera and Axio Vision software (Zeiss, Cambridge, UK).

Preprocessing, including cropping, noise reduction, and histogram adjustments, was performed using Photoshop (v13.0).

@@

Repeatability was assessed by X (comparing mulitple counted images)

Hand measures data set generated by using ImageJ/Fiji (v1.52) [@fiji].

total Sc was measured [@wang_2019_sc]

Bivalent level measure were done [@peterson_2019]

@@

Statistical analysis was performed in R (v3.5.2)[@Rstudio].

@@

$X \sim mouse average MLH1 ~ sex + subspecies + random(strain) + \xi $
 can't get the equation in the right format. I think this breaks the pdf kniting.

@@

the random effect of strain in this model can be interpreted as the average standard deviation due to the random strain effect
and sex  strain,
